What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-01-12 paper/main.tex
Added visualization discussion

>>>>

Going forward, it will become important to conduct a user survey to gather data from a representative audience of system engineers regarding what timeline visualizations help most with formula validation. Specifically, we list the following questions regarding the intuitive aesthetics of timelines.
\begin{itemize}
\item {\bf Can lines in timelines be curved or do they need to be straight?} If a timeline has a curved line is that still visually, intuitively a line? Does the placement of the line matter as to whether it is intuitive for the line to be straight or curved (e.g., to save space or reduce possible visual clutter)?

\item {\bf Can there be back edges in a limited fashion (i.e., to simplify formulas) in timelines?} Most of our formulas have star-height of 1, so if we limit the back-edge representation to only surrounding a single node, that would simplify most formulas. We can then use the expanded notation for stared formulas larger than a single proposition, thus navigating a trade-off between small representation and limiting the visual complication. Do the back edges in a limited capacity cause confusion between timeline and automata representatins?

\item {\bf What are intuitive representations of star-formulas and do they change depending on the formula?} There are two ways to represent stars in regular expressions \cite{Runming where did you find these?}. We can represent a stared formula inside a box \cite{where?} or with a back edge \cite{where?}. Does using the box cause confusion with respect to the LTL $\Box$ operator? What is the most intuitive way to remind users of the corner case where the starred formula occurs zero times?

\item {\bf When do we choose to unroll for clarity? When do we merge parallel parts of timelines?} To merge parts of lines, we have to check for logical equivalence of the parts of the timelines we want to merge. By our algorithm, we generate parallel lines only when the formulas are not syntactically equivalent, so we would be guaranteed to run the more complex check for logical equivalence. In some cases, this could provide a clarifying simplification, with the cost of a repetitive computationally expensive check. Would it make sense to offer an ``optimizing'' compilation option to users that takes longer to create a timeline representation but checks for smaller representations via logical equivalence?
\end{itemize}
KYR note: we should include a figure here with the different visual options we brainstormed and reference it in the bullets above.
